Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-09 manuscript/climate_sensitivity_SI.Rmd
minor updates to tables 4-5 and S4-S5

\newpage
```{r table S4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS4_singlevariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S4. Single-variable tests of hypothesized drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable. Models including each variable were compared to corresponding null models. Delta AICc is the AICc of the null model minus that of the model including the variable (thus, Delta AICc > 1 indicates that the variable significantly improves the model). Variable abbreviations are as in Table 2.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  # pack_rows("Tree size and microenvironment", 1, 12, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
*$\Delta$AICc > 1: variable qualified for inclusion in full model

>>>>

\newpage
```{r table S4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS4_singlevariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S4. Individual trait tests of hypothesized drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable. Models including each variable were compared to corresponding null models. Delta AICc is the AICc of the null model minus that of the model including the variable (thus, Delta AICc > 1 indicates that the variable significantly improves the model). Variable abbreviations are as in Table 2.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  # pack_rows("Tree size and microenvironment", 1, 12, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
**$\Delta$AICc > 2: variable considered significant as an individual predictor

### 2020-07-09 manuscript/tables&figures.Rmd
minor updates to tables 4-5 and S4-S5

\clearpage
```{r table 4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/table4_singlevariable_models_reform.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_all.csv`.
kable(singlevar_table, booktabs = TRUE, caption = "Table 4. Single-variable tests of hypothesized drivers of drought resistance. Models including each variable were compared to corresponding null models. Delta AICc is the AICc of the null model minus that of the model including the variable (thus, Delta AICc > 1 indicates that the variable significantly improves the model). Variable abbreviations are as in Table 2.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  # pack_rows("Tree size and microenvironment", 1, 12, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
*$\Delta$AICc > 1: variable qualified for inclusion in full model

>>>>

\clearpage
```{r table 4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/table4_singlevariable_models_reform.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_all.csv`.
kable(singlevar_table, booktabs = TRUE, caption = "Table 4. Individual trait tests of hypothesized drivers of drought resistance ($Rt$ metric). Models including each variable were compared to corresponding null models. Delta AICc is the AICc of the null model minus that of the model including the variable (thus, Delta AICc > 1 indicates that the variable significantly improves the model). Variable abbreviations are as in Table 2.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  # pack_rows("Tree size and microenvironment", 1, 12, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
*$\Delta$AICc > 1: variable qualified for inclusion in full model
**$\Delta$AICc > 2: variable qualified for inclusion in full model and considered significant as an individual predictor
